Concurrent Programming in Harmony

### 2020-10-18 book/paper.tex
Latest

\section*{Exercises}
\begin{problems}
\item \label{ex:bank} \autoref{fig:bank} shows an implementation of a bank with various
accounts and transfers between those accounts.
Unfortunately, running the test reveals that it sometimes leaves unterminated
processes.  Can you fix the problem?
\item Add a method \texttt{total()} to the solution of the previous question
that computes the total over all balances.
It needs to obtain a lock on all accounts.  Make sure that
it cannot cause deadlock.
\item Implement an extra process that checks, once, if the total of
the balances is the same as that at the beginning (using an assertion).
Is once enough to determine that no money gets lost or create, or should it do
so continually?
\end{problems}

@@

The following people contributed by making comments on or finding bugs in
early drafts of the book:
Anneke van Renesse,
Brendon Nguyen,
Saleh Hassen,
Sunwook Kim,
Trishita Tiwari,
Yidan Wang,
Zhuoyu Xu,
and
Zoltan Csaki.

>>>>

\section*{Exercises}
\begin{problems}
\item \label{ex:bank} \autoref{fig:bank} shows an implementation of a bank with various
accounts and transfers between those accounts.
Unfortunately, running the test reveals that it sometimes leaves unterminated
processes.  Can you fix the problem?
\item Add a method \texttt{total()} to the solution of the previous question
that computes the total over all balances.
It needs to obtain a lock on all accounts.  Make sure that
it cannot cause deadlock.
\item Implement an extra process that checks, once, if the total of
the balances is the same as that at the beginning (using an assertion).
Is once enough to determine that no money gets lost or created, or should it do
so continually?
\end{problems}

@@

The following people contributed by making comments on or finding bugs in
early drafts of the book:
Alex Chang,
Anneke van Renesse,
Brendon Nguyen,
Heather Zheng,
Saleh Hassen,
Sunwook Kim,
Trishita Tiwari,
Yidan Wang,
Zhuoyu Xu,
and
Zoltan Csaki.
